---
title: "Introduction"
author: '20045'
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## first function

when there are n dices and all number of the dices are k,what is the probability?

this function is aimed to solve the question above.

### explain

set X denoting the number of a dice .According to the probability theory

therefore

in Probability generating functions,so the coeff of s^k is the probability.

```{r}
dice<-function(n,k){
  x<-matrix(numeric((k+1)*(k+1)),ncol = k+1,nrow = k+1,byrow = TRUE)
  j<- 0
  while(j<=k){
    for(i in 0:n){
      if(6*i+j+n==k){x[i+1,j+1]<-(-1)^i*choose(n,i)*choose(n-1+j,n-1)/(6^n)}
    }
    j<-j+1
  }
  y<-sum(apply(x,1,sum))
  return(y)
}
```


## second function

this function is aimed to compute the probability of sensitive question.

there is black box with m1 white balls and m2 black balls.when people got a white ball,they could answer a easy and public question(say : is the birthday before July 1st);when people got a black ball,they could answer the sensitive question.

so

```{r}
sq<-function(N,n,p,m1,m2){
  y1<- n/N
  y2<- m1*p/(m1+m2)
  y3<- m2/(m1+m2)
  y<- (y1-y2)/y3
  return(y)
}
```
