---
title: "Introduction"
author: '20045'
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## first function

when there are n dices and all number of the dices are k,what is the probability?

this function is aimed to solve the question above.

### explain

set $X$ denoting the number of a dice and $g_X(s)$ denoting Probability generating functions.

According to the probability theory

$$
g_X(s)=Es^X=\Sigma s^X p(X)=\frac{1}{6}(x+...+x^6)
$$
therefore

$$
\begin{align}
g_{\sum X}(s)&=(g_X(s))^n\\
&=\frac{s^n}{6^n}(1+s+...+s^5)^n\\
&=\frac{s^n}{6^n} \frac{(1-s^6)^n}{(1-s)^n}\\
&=\frac{s^n}{6^n} \left(\sum_{i=0}^{n} C_n^i (-1)^i s^{6i}\right)\left(\sum_{j=0}^{+\infty} C_{n-1+j}^{n-1}s^j\right)
\end{align}
$$
so the coeff of $s^k$ is the probability.
```{r}
dice<-function(n,k){
  x<-matrix(numeric((k+1)*(k+1)),ncol = k+1,nrow = k+1,byrow = TRUE)
  j<- 0
  while(j<=k){
    for(i in 0:n){
      if(6*i+j+n==k){x[i+1,j+1]<-(-1)^i*choose(n,i)*choose(n-1+j,n-1)/(6^n)}
    }
    j<-j+1
  }
  y<-sum(apply(x,1,sum))
  return(y)
}
```


## second function

this function is aimed to compute the probability of sensitive question.

there is black box with m1 white balls and m2 black balls.when people got a white ball,they could answer a easy and public question(say : is the birthday before July 1st);when people got a black ball,they could answer the sensitive question.

seting A={saying yes};A1={saying yes about a easy and public question};A2={saying yes about the sensitive question};B1={answer a easy and public question};B2={answer the sensitive question}

so

$$
p(A)=p(A1)+p(A2)=p(B1)p(A|B1)+p(B2)p(A|B2)
$$

so

$$
p(A|B2)=\frac{p(A)-p(B1)p(A|B1)}{p(B2)}
$$

```{r}
sq<-function(N,n,p,m1,m2){
  y1<- n/N
  y2<- m1*p/(m1+m2)
  y3<- m2/(m1+m2)
  y<- (y1-y2)/y3
  return(y)
}
```
